### 2018-07-06 paper/7-related.tex
Add missing Eq in editDistance example
Two more tweaks

As a simple example of using a build system for memoization, we solve a textbook
dynamic programming problem~--~Levenshtein's \emph{edit
distance}~\cite{levenshtein1966binary}: given two input strings $a$ and
$b$, find the shortest series of edit operations that transforms $a$
to $b$. The edit operations are typically \emph{inserting}, \emph{deleting} or
\emph{replacing} a symbol. The dynamic programming solution of this problem is
so widely known (e.g., see~\cite{cormen2001introduction}) that we provide its
encoding in our \hs{Task} abstraction without further explanation.
We address elements of strings $a_i$ and $b_i$ by keys \hs{A}~$i$ and \hs{B}~$i$,
respectively, while the cost of a subproblem $c_{ij}$ is identified by
\hs{C}~$i$~$j$.

\begin{minted}[xleftmargin=10pt, fontsize=\small]{haskell}
data Key = A Int | B Int | C Int Int
\end{minted}
\vspace{0mm}
\begin{minted}[xleftmargin=10pt, fontsize=\small]{haskell}
editDistance :: Tasks Monad Key Int
editDistance (C i 0) = Just $ Task $ const $ pure i
editDistance (C 0 j) = Just $ Task $ const $ pure j
editDistance (C i j) = Just $ Task $ \fetch -> do
    ai <- fetch (A i)
    bj <- fetch (B j)
    if ai == bj
        then fetch (C (i - 1) (j - 1))
        else do insert  <- fetch (C  i      (j - 1))
                delete  <- fetch (C (i - 1)  j     )
                replace <- fetch (C (i - 1) (j - 1))
                return (1 + minimum [insert, delete, replace])
editDistance _ = Nothing
\end{minted}

>>>>

As a simple example of using a build system for memoization, we solve a textbook
dynamic programming problem~--~Levenshtein's \emph{edit
distance}~\cite{levenshtein1966binary}: given two input strings $a$ and
$b$, find the shortest series of edit operations that transforms $a$
to $b$. The edit operations are typically \emph{inserting}, \emph{deleting} or
\emph{replacing} a symbol. The dynamic programming solution of this problem is
so widely known (e.g., see~\cite{cormen2001introduction}) that we provide its
encoding in our \hs{Tasks} abstraction without further explanation. We address
elements of strings $a_i$ and $b_i$ by keys \hs{A}~$i$ and \hs{B}~$i$,
respectively, while the cost of a subproblem $c_{ij}$ is identified by
\hs{C}~$i$~$j$.

\vspace{0.5mm}
\begin{minted}[xleftmargin=10pt, fontsize=\small]{haskell}
data Key = A Int | B Int | C Int Int deriving Eq
\end{minted}
\vspace{0mm}
\begin{minted}[xleftmargin=10pt, fontsize=\small]{haskell}
editDistance :: Tasks Monad Key Int
editDistance (C i 0) = Just $ Task $ const $ pure i
editDistance (C 0 j) = Just $ Task $ const $ pure j
editDistance (C i j) = Just $ Task $ \fetch -> do
    ai <- fetch (A i)
    bj <- fetch (B j)
    if ai == bj
        then fetch (C (i - 1) (j - 1))
        else do insert  <- fetch (C  i      (j - 1))
                delete  <- fetch (C (i - 1)  j     )
                replace <- fetch (C (i - 1) (j - 1))
                return (1 + minimum [insert, delete, replace])
editDistance _ = Nothing
\end{minted}
\vspace{0.5mm}
